sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-12-03 doc/paper.Rmd
8->7

knitr::kable(d, format = "latex", caption = "Comparison of functionality between eight R packages that can fit geostatistical GLMMs.", 
  booktabs = TRUE, 
  linesep = c(
    rep('', 4), # coefs
    '\\addlinespace',
    rep('', 6), # correlation stuff
    '\\addlinespace',
    rep('', 12), # likelihood
    '\\addlinespace',
    rep('', 2), # bayes
    '\\addlinespace'
  ),
  escape = FALSE, row.names = FALSE) %>%
  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::footnote(
    number = c(
      "Technically possible but non-trivial",
      "Penalized smoother GAMs",
      "Spatiotemporal fields as random walk only",
      "SPDE approach as in Miller et al. (2019)",
      "Does have predictive process knots",
      "Zero-inflated NB2 only",
      "Tweedie power parameter fixed for \\\\texttt{mgcv::gamm()}",
      "Technically possible but non-trivial",
      "Technically possible but non-trivial"
    ),
    escape = FALSE
  )
```

>>>>

knitr::kable(d, format = "latex", caption = "Comparison of functionality between seven R packages that can fit geostatistical GLMMs.", 
  booktabs = TRUE, 
  linesep = c(
    rep('', 4), # coefs
    '\\addlinespace',
    rep('', 6), # correlation stuff
    '\\addlinespace',
    rep('', 12), # likelihood
    '\\addlinespace',
    rep('', 2), # bayes
    '\\addlinespace'
  ),
  escape = FALSE, row.names = FALSE) %>%
  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::footnote(
    number = c(
      "Technically possible but non-trivial",
      "Penalized smoother GAMs",
      "Spatiotemporal fields as random walk only",
      "SPDE approach as in Miller et al. (2019)",
      "Does have predictive process knots",
      "Zero-inflated NB2 only",
      "Tweedie power parameter fixed for \\\\texttt{mgcv::gamm()}",
      "Technically possible but non-trivial",
      "Technically possible but non-trivial"
    ),
    escape = FALSE
  )
```
